The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.

### 2022-09-04 src/tex/ms.tex
added prints and split CE and stable plot
changed legend and wrote a bit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{Plot_Mass_distributions.py}
\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_stable_SFRD_variations.pdf}
\caption{The primary mass distribution of merging BBH systems from the stable mass transfer channel for several variations in \SFRDzZ. 
The first five panels show variations of the cosmic metallicity density distribution  \dpdZ, eq. \ref{eq: z log skew}, (parameters listed in the first three columns of Table \ref{tab: fit params}), where we vary one parameter at a time while keeping the rest fixed at their fiducial value. The bottom right panel shows variations in the magnitude of the star formation rate with redshift; i.e. \SFRDz. For the latter we vary the four fiducial parameters of \SFRDz simultaneously (last two columns of Table \ref{tab: fit params}). All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate indicated in the legend. For reference, we show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey. We annotate the relative change in the rate at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$. 
  \label{fig: stable mass dists}}
\end{figure*}

\begin{figure*}
\centering
\script{Plot_Mass_distributions.py}
\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_CE_SFRD_variations.pdf}
\caption{Same as Figure \ref{fig: stable mass dists}, but for the Common Envelope channel. These figures show that the low mass end of the primary mass distribution is least affected by the adopted \SFRDzZ. Moreover, the \textit{location} of features in the mass distribution are robust against all explored variations.
   \label{fig: CE mass dists}
  }
\end{figure*}

@@

% The location of features is robust
The first thing we note is that the location of the features in the primary mass distribution are robust against variations in \SFRDzZ. For the CE channel, the global peak of the mass distribution remains at approximately $\Mbheen\approx16\Msun$ for all variations. 
Similarly, the stable channel displays two peaks that are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a peak at $\Mbheen\approx22\Msun$. 
Two more peaks are visible in the stable channel at the high mass end for almost all \SFRDzZ (at $\Mbheen\approx35\Msun$ and $\Mbheen\approx45\Msun$); these peaks only fade for variations where the rate of high mass BHs is generally suppressed (dashed lines in top panel of Fig. \ref{fig: stable mass dists}). 
%
This is consistent with the results in \cite{Broekgaarden+2021b}. Although peaks in the probability distribution of chirp masses as shown in their Fig. 4 can disappear when \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same. 
%
This result is furthermore consistent with recent findings in \cite{chruslinska2022_review}. In their Figure 5, they compare two very different models of \SFRDzZ and find that, although the normalisation between the two BBH merger rates is completely different, the location of the peaks remains the same. 
%
This implies that the \textit{locations} of features in the mass distribution of BBHs are determined by the formation channel and its underlying stellar and binary physics. The location of features could therefore serve as sign posts of the underlying physics.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{Plot_StableMass_distributions.py}
\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_stable_SFRD_variations.pdf}
\caption{The primary mass distribution of merging BBH systems from the stable mass transfer channel for several variations in \SFRDzZ. 
The first five panels show variations of the cosmic metallicity density distribution  \dpdZ, eq. \ref{eq: z log skew}, (parameters listed in the first three columns of Table \ref{tab: fit params}), where we vary one parameter at a time while keeping the rest fixed at their fiducial value. The bottom right panel shows variations in the magnitude of the star formation rate with redshift; i.e. \SFRDz. For the latter we vary the four fiducial parameters of \SFRDz simultaneously (last two columns of Table \ref{tab: fit params}). All panels are shown at a reference redshift of $z=0.2$, with the corresponding predicted BBH merger rate indicated in the legend. For reference, we show the power-law + peak model from \protect\cite{GWTC3_popPaper2021} in grey. We annotate the relative change in the rate at three reference masses: $10\Msun$, $25\Msun$ and $40\Msun$. 
  \label{fig: stable mass dists}}
\end{figure*}

\begin{figure*}
\centering
\script{Plot_CEMass_distributions.py}
\includegraphics[width=0.8\textwidth]{figures/Mass_distributions_CE_SFRD_variations.pdf}
\caption{Same as Figure \ref{fig: stable mass dists}, but for the Common Envelope channel. These figures show that the low mass end of the primary mass distribution is least affected by the adopted \SFRDzZ. Moreover, the \textit{location} of features in the mass distribution are robust against all explored variations.
   \label{fig: CE mass dists}
  }
\end{figure*}

@@

% The location of features is robust
The first thing we note is that the location of the features in the primary mass distribution are robust against variations in \SFRDzZ.
For the stable channel, two features are visible in all variations: a peak at $\Mbheen\approx9\Msun$ and a bump at $\Mbheen\approx22\Msun$. 
Two more features are visible in the stable channel at the high mass end for almost all \SFRDzZ (a knee at $\Mbheen\approx35\Msun$ and another bump at $\Mbheen\approx45\Msun$). Athough the locations of these features are constant, these features disappear for variations of  the metallicity-dependent cosmic star formation history where the rate of high mass BHs is suppressed (e.g., dashed lines in the top panels of Fig. \ref{fig: stable mass dists}).  
Similarly, the CE channel displays a kink in the distribution at about $9\Msun$, and a peak at approximately $\Mbheen\approx17\Msun$ for all variations. The latter peak is the global peak of the mass distribution in almost all variations.

The finding that the locations of features in the mass distribution do not change for different \SFRDzZ is consistent with earlier work. 
%
Recent work by \cite{chruslinska2022_review} showed that, when comparing two very different models of \SFRDzZ (their Figure 5), the location of the peaks remains the same, even though the normalisation between the two BBH merger rates is completely different. 
%
\cite{Broekgaarden+2021b} furthermore showed that variations in the \SFRDzZ can induce variations in the rate that are off the same order of magnitude as the variations caused by uncertainties in the binary physics. In their Fig. 4, they show the probability distribution of chirp masses for BBHs. Although features can disappear when \SFRDzZ prohibits the formation of certain (typically higher) mass BHs, the \textit{location} of features remains the same
%
This implies that the locations of features in the mass distribution of BBHs are determined by the formation channel and its underlying stellar and binary physics. The locations of features could therefore serve as sign posts of the underlying physics. \\
